%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.5in,right=0.75in,bottom=0.5in]{geometry} % Document margins

\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Joshua Sun} % Your name
\mobile{(+1) 415-881-0388}
\email{joshuasun1998@icloud.com}
\homepage{joshsun.ca}
\github{jsun98}

\begin{document}

%----------------------------------------------------------------------------------------
%	Skills SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Qualifications}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Languages: & Java, Python, JavaScript, C/C++ \\
Machine Learning: & Vowpal Wabbit, TensorFlow, Scikit-learn, Gradient Boosting Decision Trees (GBDT) \\
Big Data Analysis: & Hadoop, MapReduce, HDFS, Hadoop-Streaming, Pig, Oozie, Storm, Avro \\
Tools: & Git, Maven, Docker, Travis CI, Screwdriver, Jenkins, Heroku \\
Databases: & MySQL, MongoDB, NoSQL \\
\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

\begin{expSec}
{Yahoo!}
{Backend Software Engineer | Mail Anti-Spam}
{Sunnyvale, California}
{The Anti-spam team analyzes \textbf{tens of billions} of SMTP requests daily for Yahoo!, AOL. and Oath.}
{Jan 2018 - Apr 2018}
\item Designed a spam classifier using \textbf{gradient boosting trees}, which scored a \textbf{97.28\%} accuracy on 240 billion test data points, resulting in \textbf{184 million additional spams} captured daily.
\item Built a \textbf{terabyte-scale} distributed machine learning data pipeline on Hadoop and wrote a series of MapReduce jobs in Java and Pig for data generation, feature selection, model training and model evaluation.
\item Scaled Vowpal Wabbit and GBDT libraries to \textbf{parallel train on 10 billion training examples} in under 30 minutes by using Hadoop-Streaming and the Spanning Tree, reducing training latency \textbf{by 280\%}.
\item Designed an \textbf{Apache Storm} duplicate detection bolt using Guava Cache for an online spam detection algorithm, increasing throughput of the cloud message queue by 65\%.

\end{expSec}

\begin{expSec}
{MentorMap}
{Co-Founder \href{https://www.mentormap.ca/}{\space\small\faExternalLink}}
{Toronto, Ontario}
{MentorMap is a startup that connects prospective students with current university students.}{May 2017 - Nov 2017}
\item Architected a \textbf{video scheduling web app} for mentors and mentees using Node.js, MongoDB, HTML and CSS.
\item Designed a scalable MongoDB/Mongoose model that avoided transactions by using embedded documents.
\item Led a team of 5 in software development and marketing and recruited \textbf{100+ members}.
\end{expSec}

\begin{expSec}
{OMERS}
{Full Stack Developer | Test Automation Team}
{Toronto, Ontario}
{OMERS is Canada's largest pension fund with \$72 billion in net assets.}
{May 2017 - Aug 2017}
\item Developed React/Redux/Node.js web applications to simplify the mock data creation workflow for 40 testers.
\item Optimized the Selenium Grid infrastructure to efficiently run tests in parallel, reducing runtime by 45\%. \end{expSec}

\end{rSection}


%----------------------------------------------------------------------------------------
%	PROJECTS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Projects}

\begin{projSec}{Stock Predictor + Trade-bot}{}{Python, TensorFlow, Scikit-learn, MySQL \href{https://github.com/UWCESEDUO/stock-prediction}{\space\faGithub}}
\item Applied supervised learning methods such as Neural Networks, Random Forest and Gradient Boosting regressors to forecast the S\&P 500 stock prices based on past returns and financial indicators.
\item Developed a simulation trade-bot that buys and sells stocks based on the model forecasts.
\end{projSec}

\begin{projSec}{Lacs/LISP Compilers}{}{Scala, C++ \href{https://github.com/jsun98/SchemePlusPlus}{\space\faGithub}}
\item Implemented the CYK parsing algorithm, heap/stack memory management and a garbage collector.
\end{projSec}

\end{rSection}


%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

\subsectiontitlestyle{University of Waterloo}{}{Sep 2016 - Apr 2021}{}
\vspace{-1em}
\\ Bachelor of Software Engineering, Joint Combinatorics and Optimization \hfill {GPA: 3.70 }

\end{rSection}

%----------------------------------------------------------------------------------------
%	HONORS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Honors}

\begin{honorSec}{6th Place @ YHack}{Competed against 115 teams at the Yale University hackathon}{Dec 2017}\end{honorSec}
\begin{honorSec}{Governor General's Academic Medal}{Highest GPA in high school of 439 students}{Jun 2016}\end{honorSec}
\vspace{1em} 

\end{rSection}

\end{document}
