%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Automation Developer \tiny\textbf{(Outstanding Employer Evaluation)}} % Job title
    {OMERS Corporation \tiny - An Ontario Pension Fund with \$72 Billion in Net Assets.} % Organization
    {Toronto, Canada} % Location
    {May. 2017 - Aug. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Implemented the Selenium Grid framework using Java that enabled multi-environment, distributed test execution on 5 different Jenkins servers, which increased the number concurrent test executors from 2 to 10.}
         \item {Refactored, debugged and documented a total of 32 test scripts to use the new framework, resulting in a 20\% increase in productivity.}
        \item {Developed several MERN stack RESTful web apps that automated the test data creation process by running them in large batches instead of manually. Currently serving 50 internal users and saving each person over 10 hours of time every weekly.}
        \item {The first co-op student to be recognized and awarded by the Vice President of IT for unique contributions to the automation team.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Co-Founder \& Full-Stack Developer} % Job title
    {MentorMap 
    \href{https://www.mentormap.ca}{\faLink\acvHeaderIconSep}
      \tiny A student-run startup focused on connecting high school mentees with university 			mentors, currently has 105 members.}
    {Toronto, Canada} % Location
    {April. 2017 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed a complex web stack in NodeJS/MongoDB/HTML/CSS from scratch that helps schedule mentoring sessions; featuring an event scheduler, customer service chatbot, PayPal integration, video conferencing service, and automated server maintenance.}
        \item {Coordinated several mentor recruitment sessions, competed in a start-up funding pitch competition, and led weekly team meetings.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Embedded Software Developer \tiny\textbf{(98/100 Employer Evaluation)}} % Job title
    {CrossWing Robotics \href{http://www.crosswing.com/}{\faLink\acvHeaderIconSep}
    \tiny Local start-up developing patented telecommunications robots for both the U.S. and Canadian markets.} % Organization
    {Markham, Canada} % Location
    {Sept. 2014 - Feb. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed an obstacle avoidance system using ultrasonic sensors and built an Android App to track the robot's position in real time.}
        \item {Refactored, documented and tested a large C++ driver codebase for a Leap Motion robotic arm and fixed 65/67 known bugs.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
