%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}
\begin{cventries}

%---------------------------------------------------------
  \cvproject
    {} % Job title
    {RealGen \href{https://github.com/jsun98/RealGen}{\faGithub\acvHeaderIconSep} 
    \tiny NodeJS, MongoDB, React, Heroku Cloud} % Organization
    {} % Location
    {Aug. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Generates real estate advertisement website templates based on MLS number (unique serial code for each listing), featuring full MLS integration, SEO, Paypal checkout, and automatic data injection to avoid filling each template with data manually.}
         \item {Used by 22 real estate agents on a daily basis, each saving over \$25 per site and hours of time.}
      \end{cvitems}
    }
    
    %---------------------------------------------------------
  \cvproject
    {} % Job title
    {Jenkins Automation Dashboard \href{https://github.com/jsun98/Jenkins-Automation-Dashboard}{\faGithub\acvHeaderIconSep}
    \tiny NodeJS, MongoDB, React, Heroku Cloud} % Organization
    {} % Location
    {July 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Data visualization tool with attractive graphics for visualizing results of automated tests to non-technical members of the team.}
        \item {Currently used for categorizing 4000+ test results for the PMO team at OMERS weekly meetings, shortening meeting time by over 15\%.}
      \end{cvitems}
    }


%---------------------------------------------------------
  \cvproject
    {} % Job title
    {LISP/Scheme Interpreter \href{https://github.com/jsun98/SchemePlusPlus}{\faGithub\acvHeaderIconSep} \tiny C++} % Organization
    {} % Location
    {June 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {A miniature interpreter written in C++ using lexical analysis and REPL. Heavy use of OOP, function pointer and hashmap concepts.}
      \end{cvitems}
    }





%---------------------------------------------------------
%---------------------------------------------------------
%---------------------------------------------------------
  \cvproject
    {} % Job title
    {RogueOne \href{https://github.com/jsun98/RogueOne}{\faGithub\acvHeaderIconSep}
    \tiny C++, Tiva Microcontroller, Accelerometer} % Organization
    {} % Location
    {Dec. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Enhancement of the RPG game, controlled by a Tiva accelerometer. Featuring auto-scaling AI difficulty and a map generation algorithm.}
      \end{cvitems}
    }



%---------------------------------------------------------
%---------------------------------------------------------
  \cvproject
    {} % Job title
    {Clash of Civilizations App \tiny Android API, Kotlin, AWS} % Organization
    {} % Location
    {Ongoing} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {A Civilization-like turn-based multiplayer strategy game played on a world map with each player/nation fighting for world dominance.}
        \item {Will feature smart AI opponents with unique personalities, battle strategies and foreign policies.}
         \item {Planning on implementing a genetic algorithm to train AIs at each difficulty level.}
      \end{cvitems}
    }



%---------------------------------------------------------
\end{cventries}